Macro Impacts

### 2016-07-13 Macro Impacts Revised.tex
Update

These are arcs of circles which touch the boundary $r=\f ab$ at right angles. That is, the trajectory of rays is given by geodesics in the Poincare disk. This can be seen easily by inspection of the metric a modified Poincare Disk:

@@

>>>>

These are arcs of circles which touch the boundary $r=\f ab$ at right angles. That is, the trajectory of rays is given by geodesics in the Poincare disk. This can be seen easily by inspection of the metric a modified Poincare Sphere:

@@

It is then obvious that $b=0$ corresponds to straight lines. The importance of this observation is that $b\approx 10^{-7}\te{s}^{-1}$ and $a\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $10^8\te{km}$, while the earth is of radius $10^3\te{km}$. Hence, the smallest radius of curvature of an arc will be roughly $10^{-5}\te{km}$. Thus, it is a reasonable first approximation to take the seismic waves to propagate in straight lines.
